# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data

Download and unzip the file
```{r}
temp <- tempfile()
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp)
data <- read.csv(unz(temp, "activity.csv"), na.strings="NA", stringsAsFactors + )
unlink(temp)
```

convert "date" to a date field
```{r}
data$date=as.Date(data$date)
```

Add leading zero's to the interval field
```{r}
data$interval=formatC(data$interval, width=4, format="d", flag="0")
```

Add a column that is the date and time (interval plus date in datetime format)
```{r}
data$time <- strptime(paste(data$date, data$interval), format = "%Y-%m-%d %H%M")
```

## What is mean total number of steps taken per day?

Create a total of steps by day, then plot the histogram
```{r}
totalbyday=aggregate(steps~date, data, FUN=sum)
hist(totalbyday$steps)
```

Calculate the mean number of steps per day
```{r}
mean(totalbyday$steps)
```

Calculate the median number of steps per day
```{r}
median(totalbyday$steps)

```

## What is the average daily activity pattern?
Create average steps by interval
```{r}
avgsteps=aggregate(steps~interval, data, FUN=mean)
plot(avgsteps$interval, avgsteps$steps, type="l")
```

Calculate the 5 Minute interval with the highest number of average steps
```{r}
avgsteps[(which.max(avgsteps$steps)),]
```


## Imputing missing values
Ttotal number of rows with NAs
```{r}
data$isNA=is.na(data$steps)
sum(data$isNA)
```

Imputing missing data
```{r}
imputed=merge(x=data, y=avgsteps, by="interval", all.x=TRUE)
imputed$imp=ifelse(is.na(imputed$steps.x), imputed$steps.y, imputed$steps.x)
```

Redo Histogram, mean and median with the imputed values
Create a total of steps by day, then plot the histogram
```{r}
totalbydayImp=aggregate(imp~date, imputed, FUN=sum)
hist(totalbydayImp$imp)
```

Calculate the mean number of steps per day
```{r}
mean(totalbydayImp$imp)
```

Calculate the median number of steps per day
```{r}
median(totalbydayImp$imp)
```


## Are there differences in activity patterns between weekdays and weekends?

